\documentclass[
    jphafner,
    fontsize=11pt,
    foldmarks=false,
    pagenumber=false,
    addrfield=true,
]{scrlttr2}

%\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{palatino}
%\usepackage{charter}
%\usepackage{lmodern}
%\usepackage{polyglossia}
%\setdefaultlanguage[variant=american]{english}


%\usepackage[en]{babel}
%\usepackage{blindtext}
%\usepackage{lipsum}
\usepackage{hyperref}

\date{\today}
%\setkomavar{subject}{Data Scientist}
%\setkomavar{subject}{Network Administrator}
\setkomavar{subject}{High School Teacher (2019-2020), Promise Academy (High Compensation+Bonus)}

\begin{document}

\begin{letter}{Harlem Children's Zone}
		%High School Teacher (2019-2020), Promise Academy (High Compensation+Bonus)
    \opening{Dear Promise Academy, Harlem Children's Zone:}
%\begin{letter}{Syracuse Research Corporation---Rome, NY}
%    \opening{Dear Syracuse Research Corporation, INC.:}

    I am applying for your open position of Physics Teacher.
    %I am looking forward to relocating to New York City for such opportunities.

    %I have not worked for almost a full year, because I had a brain lesion, and stroke.
    %I have just recently been approved for work.

    I have taught High School physics for two years.
    I have worked tirelessly on \href{https://github.com/jphafner/physicsAMC}{physicsAMC}, my project to give students infinite redos.
    %I have enclosed two letters of reference, and my teaching philosphy.

    %With a unique combination of education and hands-on IT experience, I am confident that I will make an immediate and impactful contribution as your Business Data Analyst at Turning Stone Casino.
    
 Most recently, I was a Unix Systems Engineer at IPsoft, Inc. of New York NY,
    where I work closely with major clients to monitor their IT infrastructure needs. 
    I closely monitored client systems, and developed automated solutions in response to their unique requirement.
    My experience is complimented by a Ph.D. in Physics and certifications from Red Hat and Cisco.

%I have passed the P and FM SOA exams, so I am familiar with the math involved.
My dissertation was in computational biophysics, so I am very proficient with programming.
    I have a lot of experience using Python, with scipy and numpy.
    I was very active as a teacher programming, \url{www.github.com/jphafner/physicsAMC},
        at Baltimore City Schools and Masters for two years.
    %For an example lesson plan, and template lab report, please look here
    %    \url{www.github.com/jphafner/physicsReport}.

%I have five years of experience as a Systems Engineer, three as a volunteer during my doctorate, and two at IPsoft.
    %I have five years of experience with C, and ten with Python.
    %I have experience with OpenLDAP, Kerberos, OpenAFS during my doctorate.
    %I have create \hyperref[www.github.com/jphafner/physicsAMC]{physicsAMC}
    %I have created 

My achievements can be attributed to my ability to respond effectively to constantly-changing in fast-moving, often hectic environments. 
    I'm known as a polished communicator and motivated professional, and I strike to continuously deliver beyond expectations.


I encourage you to read further about my background in the accompanying resume. 
    I welcome an interview with you and look forward to what I anticipate will be the first of many positive communications. 
    Thank you in advance for your time and consideration.

%% Closing remarks
    %I can begin in March of next year, due to having a brain tumor, and appointments with the \href{https://www.dana-farber.org}{Dana-Farber Cancer Institute}.
    %This is also why I have not worked in a while.

%I can use Fred Parker and Ray Halbritter as references.

\closing{Sincerely:}
%\encl{R\'{e}sum\'{e} and Business card}
\end{letter}
\end{document}

