%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Writing}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cvhonor
    {Finalist} % Award
    {DEFCON 25th CTF Hacking Competition World Final} % Event
    {Las Vegas, U.S.A} % Location
    {2017} % Date(s)

	\cvhonor
     {Hafner J \& Zheng W. Approximate normal mode analysis based on vibrational subsystem analysis with high accuracy and efficiency. J. Chem. Phys. 130, 194111 2009.  \href{http://www.acsu.buffalo.edu/~wjzheng/Hafner_jcp2009.pdf}{(pdf)}}
  \twentyitemshort
     {2010}
     {Hafner J \& Zheng W. Optimal modeling of atomic fluctuations in protein crystal structures for weak crystal contact interactions. J. Chem. Phys. 132, 014111 2010. \href{http://www.acsu.buffalo.edu/~wjzheng/Hafner_jcp2010.pdf}{(pdf)}}
  \twentyitemshort
     {2011}
     {Hafner J \& Zheng W. All-atom modeling of anisotropic atomic fluctuations in protein crystal structures. J. Chem. Phys. 135, 144114 2011 \href{http://www.acsu.buffalo.edu/\~{}wjzheng/Hafner_jcp2011.pdf}{(pdf)}}

%---------------------------------------------------------
  \cventry
    {Founder \& Writer} % Role
    {A Guide for Developers in Start-up} % Title
    {Facebook Page} % Location
    {Jan. 2015 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Drafted daily news for developers in Korea about IT technologies, issues about start-up.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Undergraduate Student Reporter} % Role
    {AhnLab} % Title
    {S.Korea} % Location
    {Oct. 2012 - Jul. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Drafted reports about IT trends and Security issues on AhnLab Company magazine.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
